### 2017-03-30 ThesisText/final.tex
Adds conclusions and future work

% =============================================================================
\section{This Project}
\TODO{}

@@

In this project it was shown how the original data from the University of
Évora's Moodle was preprocessed into a data repository useful for analysis.
Some statistics over that data were then shown.

The techniques applied are divided into Supervised and Unsupervised learning. In supervised learning

% =============================================================================
\section{Future Work}
\TODO{}

>>>>

@@

In this project it was shown how the original data from the University of
Évora's Moodle was preprocessed into a data repository useful for analysis.
Some statistics over that data were then shown. The experiments were broken
down by dataset. Each dataset was build from the pre processed original data.

The techniques applied are divided into Supervised and Unsupervised learning.
In supervised learning, Decision Trees and Naive Bayes Classifiers were
applied. In unsupervised learning, clustering was done using the K-Means and
the Affinity Propagation algorithms.

% =============================================================================
\section{Supervised Learning Tasks}

Supervised learning techniques were applied to the different variants of the
three described datasets. For every one of them, Decision Trees and Naive Bayes
Classifiers were trained using the cross validation technique described in
section~\ref{sec:cross_val}.

It was shown how these models were generally able to achieve high values of
accuracy. This means that it is possible to:

\begin{enumerate}
    \item Predict student grades from their usage of Moodle;
        (Section~\ref{sec:exp_001})
    \item Predict how many courses is a student going to complete given he's
        usage of Moodle and initial number of enrolled courses;
        (Section~\ref{sec:exp_003})
    \item Predict student grades from his usage of features in Moodle.
        (Section~\ref{sec:exp_005})
\end{enumerate}

Following cross validation, each model was trained ten times, each training is
done with nine folds from the dataset, leaving one fold for testing. Despite
having high values for maximum accuracy, and relatively high values for average
accuracy, some models show very low values for minimum accuracy. This means
that some instances of training have testing folds which are too different from
the folds used in training, and therefore, the testing folds may contain
outlier objects.

Continuing the analysis in this project, it might be important to understand
which are these outlier cases in order to achieve better accuracies in further
supervised learning tasks.

% =============================================================================
\section{Unsupervised Learning Tasks}

Clustering tasks were done and it was shown that some separation of objects
exists in the explored datasets. Results for experiment~\ref{sec:exp_004},
which are about course completion given the number of enrolled courses and
Moodle usage data, were particularly promising because the results show a
maximum and average silhouette score above 0.70 for two, three, and four
clusters.

Clustering was also done by dividing the data into folds of ten and excluding
one fold for each training execution, and then using that fold to calculate the
silhouette score. The difference between the maximum and minimum silhouette
scores using this division method were noted to be minimal, sometimes not
exceeding a value of 0.05.

In these unsupervised learning tasks, the K-Means algorithm was used along with
Affinity Propagation. However, only K-Means produced good results for
silhouette scores.

From these results, two things can be further done. First, the clustering
results may be analysed in order to understand what are the characteristics of
each cluster of the more successful tasks. In section~\ref{sec:exp_002}, for
example, we see that data seems to be divisible into two clusters. An
hypothesis for this binary division may be that one cluster contains objects in
which students get approved in courses while the other cluster contains the
opposite.

In section~\ref{sec:exp_004}, like mentioned above, we see good scores for two,
three, and four clusters. However, without further analysis, no hypothesis is
presented at this time as to what are the reasons we see such good separation
of objects in this dataset.

Aside from those analysis, one second thing to do is to use different
clustering algorithms. One algorithm to use would be K-Modes, which is a
variant of K-Means useful for nominal data, which is present in this data.

% =============================================================================
\section{Applications}

The results of an~\gls{edm} study may have many applications. Experiments such
as the ones made to dataset~\ref{sec:exp_001_002} and~\ref{sec:exp_005_006}
yield insight into how the basic usage of Moodle is a great indicator of the
success of students. From the trained models, future applications may be
develop which look into students and their usage of Moodle and finally predict
their success even before a student as finished a course. With such
applications we can detect student behaviour that might lead to his failure of
a course and signal that student to take action to avoid failure.

From the Moodle data described in this project, further classification and
clustering analysis may also be done. Mode Datasets may be built and analyse from
the original data and more algorithms may be used. For example, a dataset may
be built that joins Moodle usage data (as described in
sections~\ref{sec:exp_001_002} and~\ref{sec:exp_005_006}) and profiling data
(as described in section~\ref{sec:exp_003_004}). A dataset with all these
fields might yield better accuracies in the prediction of grades or more ways
to do clustering.

Finally, other types of Data Mining analysis may be done. For example, in the
background section, Neural Networks are mentioned to be a usual model
in~\gls{edm} for grade prediction. Association Rule Analysis, which is a topic
not discussed in this project, may also be used with this data. Possibly,
dependencies between course completion features might be detected.
